### 2021-07-05 chapters/7_discussion.tex
added results exp1

\chapter{Discussion}
\label{ch:discussion}
In this chapter, we discuss the results of our experiment(s) on ...

@@

\section{Threats to validity}
What could affect the validity of your research? Think of pitfalls of your research method, experimental setup, interpreting the results.

>>>>

\chapter{Discussion}
\label{ch:discussion}
In this chapter, we discuss the results of our experiments on clustering the mutants.

@@

\section{Threats to validity}
What could affect the validity of your research? Think of pitfalls of your research method, experimental setup, interpreting the results.
- pit generated mutants -> it's hard to know if we can cluster ALL posible mutants
- Selected sources
- equivalent mutants
